Extreme heterogeneity of influenza virus infection in single cells

### 2018-01-15 paper/paper.tex
one last manuscript comment

\figsupp[Many genes that co-vary with viral load are involved in the oxidative stress response. \label{figsupp:ROStable}]{
Table delineating genes in \FIG{cellulargenes} that are associated with the response to oxidative stress~\citep{Duong:2017ju,Jung:2017jz,Lee:2017ba,Peuchant:2017hj,MacLeod:2016kt,Jiang:2016cf,Gorrini:2013jv,Miura:2013fr,Kim:2009gi,Banning:2005cz,Murray:2003ie,Doyle:1999ts}.
}{\includegraphics[width=0.7\linewidth]{figures/ROStable.pdf}}

>>>>

\figsupp[Many genes that co-vary with viral load are involved in the oxidative stress response. \label{figsupp:ROStable}]{
\jdbcomment{Alistair, can you remove GPX2, which is no longer significant.}
Table delineating genes in \FIG{cellulargenes} that are associated with the response to oxidative stress~\citep{Duong:2017ju,Jung:2017jz,Lee:2017ba,Peuchant:2017hj,MacLeod:2016kt,Jiang:2016cf,Gorrini:2013jv,Miura:2013fr,Kim:2009gi,Banning:2005cz,Murray:2003ie,Doyle:1999ts}.
}{\includegraphics[width=0.7\linewidth]{figures/ROStable.pdf}}
